Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-03-20 text/paper2/ms.tex
acknowledgements

\acknowledgements
Rix, Bovy\\
Aspen?\\
Gaia data challenge / Surrey / Gaia data team / Anthony Brown \\ % check with AB about citations
APW: NSF GRFP, Sigma Xi\\
Astropy\\
Columbia HPC\\
DWH was partially supported by NASA (Grant NNX12AI50G) and the NSF (Grant IIS-1124794).

>>>>

\acknowledgements
Rix, Bovy\\
Gaia data challenge / Surrey / Gaia data team / Anthony Brown \\ % check with AB about citations
APW is supported by a National Science Foundation Graduate Research
Fellowship under Grant No.\ 11-44155. This work was supported in part by 
the National Science Foundation under Grant No. PHYS-1066293 and the 
hospitality of the Aspen Center for Physics.\\
DWH was partially supported by NASA (Grant NNX12AI50G) and the NSF (Grant IIS-1124794).\\
This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy13}. \\
Columbia HPC\\
